Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2014-08-09 ms.tex
more minor editing/clean-up prior to submission

\begin{figure}
\begin{center}
\epsfig{file=resid_offs.eps, width=3.3in}
\caption{\label{fig:resid_offs} Two-component reddening residuals after 
restricting to high ecliptic latitude ($|\beta|>20^{\circ}$) and perturbing the
\texttt{i100} and 857 GHz zero levels by $+$0.08 MJy/sr and $-$0.08 MJy/sr 
respectively. The bending behavior as a function of $E(B-V)_{SFD}$ has been
eliminated, and virtually no temperature dependence remains.}
\end{center}
\end{figure}

@@

% could add a last sentence trying to soften this, acknowledging that 
% planck team warned about their model below 353 GHz

>>>>

\begin{figure}
\begin{center}
\epsfig{file=resid_offs.eps, width=3.3in}
\caption{\label{fig:resid_offs} Two-component reddening residuals after 
restricting to high ecliptic latitude ($|\beta|>20^{\circ}$) and perturbing the
\texttt{i100} and 857 GHz zero levels by $+$0.08 MJy/sr and $-$0.08 MJy/sr 
respectively. The bending behavior as a function of $E(B-V)_{SFD}$ has been
eliminated, and virtually no temperature dependence remains. For 
$E(B-V)_{SFD}$$\gtrsim$0.3 mag, the top plot appears noisy because there are an
insufficient number of remaining SSPP points of comparison following our cut on
ecliptic latitude..}
\end{center}
\end{figure}

@@

% do i want to caution people not to extrapolate our 2comp model to higher
% frequencies, similar to what planck team did in their sec. 7.2.1 ??
